---
title: "Errata"
subtitle: "On Coppock and Green (2016), *American Journal of Political Science* 60(4)"
format:
  pdf:
    output-file: coppock_green_2016_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
library(knitr)
here::i_am("errata.qmd")

# Every number in the corrected sentences and in the notes beneath them is computed here,
# from the maintained pipeline's output, at the time this document is rendered. Nothing
# below is typed. Where a correction quotes a published cell rather than a recomputed
# one, it is read from the transcription of the printed page.
out <- function(f) read_csv(here("maintained", "output", f), show_col_types = FALSE)

rd <- out("tables_4_5_rd_all.csv")
migration <- out("table_a2_migration.csv")
coefficients <- out("table_7_coefficients.csv")
pair_metadata <- out("table_7_metadata.csv")
like_elections <- out("text_like_elections.csv")

published_appendix <- read_csv(here("ground_truth", "published_appendix_values.csv"),
                               col_types = cols(.default = col_character()))
published_maintext <- read_csv(here("ground_truth", "published_maintext_tables.csv"),
                               col_types = cols(.default = col_character()))
n_published_cells <- nrow(published_appendix) + nrow(published_maintext)

f3 <- function(x) sprintf("%.3f", x)
f4 <- function(x) sprintf("%.4f", x)

spell <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
             "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen",
             "seventeen", "eighteen", "nineteen", "twenty")
  stopifnot(n >= 1, n <= length(words))
  words[n]
}

# Entry 1: the primary-on-primary standard error.
pp <- like_elections |> filter(upstream_type == "primary", downstream_type == "primary")
pg <- like_elections |> filter(upstream_type == "primary", downstream_type == "general")
pp_z <- pp$estimate / pp$std_error
pp_published_se <- 0.0010
pp_z_published <- pp$estimate / pp_published_se

# Entry 2: Table A2's Iowa row.
a2_rd <- rd |>
  filter(years_window == "08-12", !state %in% c("meta", "FL05", "MO05"), !is.na(cace)) |>
  select(state, rd_cace = cace)
a2_published <- published_appendix |>
  filter(float == "table_a2") |>
  select(state = row_label, column_label, value_paper) |>
  pivot_wider(names_from = column_label, values_from = value_paper)
a2_check <- migration |>
  left_join(a2_rd, by = "state") |>
  left_join(a2_published |> transmute(state, published_cace = as.numeric(`CACE 08-12`)),
            by = "state") |>
  mutate(same = published_cace == round(rd_cace, 3))
state_names <- c(AR = "Arkansas", CT = "Connecticut", IA = "Iowa", IL = "Illinois",
                 FL = "Florida", KY = "Kentucky", MO = "Missouri", MT = "Montana",
                 NJ = "New Jersey", NV = "Nevada", NY = "New York", OK = "Oklahoma",
                 OR = "Oregon", PA = "Pennsylvania", RI = "Rhode Island")
wrong_state <- a2_check |> filter(!same) |> mutate(name = state_names[state])
stopifnot(nrow(wrong_state) == 1)
iowa <- migration |> filter(state == wrong_state$state)
iowa_published <- a2_published |> filter(state == wrong_state$state)

a2_corrected <- migration |>
  transmute(
    State = state,
    `Net Migrants` = sprintf("%.0f", net_migrants_100),
    `$N_c$ 2008` = sprintf("%.0f", N_c_08),
    `CACE 08-12` = f3(cace),
    `Bias Estimate` = f3(bias_estimate),
    `Corrected CACE` = f3(corrected_estimate)
  )

# Entry 3: the counts in the lower panel of Table 4.
mop <- rd |>
  filter(state != "meta", !is.na(cace),
         years_window %in% c("94-96", "98-00", "02-04", "06-08", "10-12"))
pom <- rd |>
  filter(state != "meta", !is.na(cace),
         years_window %in% c("92-94", "96-98", "00-02", "04-06", "08-10"))
oregon_only <- setdiff(
  mop$state[mop$years_window == "06-08"], pom$state[pom$years_window == "04-06"]
)

# Entry 4: battleground status of the five strongest 2008-12 estimates.
battleground <- pair_metadata |>
  filter(downYear == 2012) |>
  distinct(state_clean, battleground_P, downstream_margin)
five_strongest <- rd |>
  filter(years_window == "08-12", state != "meta", !is.na(cace),
         !str_detect(state, "05$")) |>
  arrange(desc(cace)) |>
  slice_head(n = 5) |>
  left_join(battleground, by = c("state" = "state_clean")) |>
  mutate(name = recode(state, AR = "Arkansas", NV = "Nevada", CT = "Connecticut",
                       MO = "Missouri", NJ = "New Jersey"))
battlegrounds_among_five <- five_strongest |>
  filter(battleground_P == 1) |>
  arrange(downstream_margin)
nonbattlegrounds_among_five <- five_strongest |> filter(battleground_P == 0)
# Each state carries its own margin; sorting the two columns separately would pair them
# in the wrong order.
battleground_phrases <- str_glue_data(
  battlegrounds_among_five,
  "{name} at {sprintf('%.1f', 100 * downstream_margin)} points"
)

# Entry 5: the battleground coefficient across columns 2 and 3 of Table 7.
coefficient <- function(name, model_no, column) {
  row <- coefficients |> filter(term == name, model == model_no)
  stopifnot(nrow(row) == 1)
  row[[column]]
}
bg_ratio <- coefficient("battleground_P", 2, "estimate") /
  coefficient("battleground_PM", 3, "estimate")

# Entry 6: the number of states in Table A2.
n_a2_states <- nrow(migration)

# Entry 7: the general-on-general pairs and where they are reported.
gg_pairs <- like_elections |>
  filter(upstream_type == "general", downstream_type == "general") |>
  pull(n)
t6_pairs <- out("table_6_rd_persistence.csv") |>
  filter(type == "state", !is.na(cace), !str_detect(state, "05$")) |>
  nrow()

# Entry 8: the mislabelled panel of Table A4.
analysis_states <- setdiff(unique(str_remove(rd$state, "05$")), "meta")
```

```{r entries}
# Entry 10: the 2SLS leverage behind the discontinuity standard errors.
# The cells this entry corrects are exactly the cells on which the deposit and the
# maintained pipeline disagree at the precision the tables print, so they are READ OFF
# THE GROUND TRUTH'S OWN VERDICT rather than named here. Every other entry recomputes
# from maintained/output; this one cannot, because what it describes is a disagreement
# between two computations and the ground truth is where that comparison lives.
#
# THE APPENDIX'S SIX CELLS ARE THE SAME CAUSE, adjudicated 2026-09-12. They were held out
# of this entry on the reasoning that leverage cannot touch a point estimate. That is true
# of a state's own estimate and false of a pooled one: Tables A6 and A7 print fixed-effects
# meta-analytic CACEs, and a fixed-effects meta-analysis is inverse-variance weighted, so
# its weights ARE the state standard errors the convention moves.
ground_truth <- read_csv(here("ground_truth", "coppock_green_2016_ground_truth.csv"),
                         show_col_types = FALSE)
leverage_tables <- c("Table 4", "Table 5", "Table 6", "Table 7", "Table A6", "Table A7")
leverage_cells <- ground_truth |>
  filter(table_figure %in% leverage_tables, match == 1, match_rewrite == 0) |>
  arrange(table_figure, claim) |>
  mutate(
    label     = claim |> str_replace(", se$", ", SE") |> str_replace(", est$", ", estimate"),
    published = str_glue("{table_figure}, {label}: [[{value_paper}]]"),
    corrected_value = sprintf(paste0("%.", digits, "f"), value_rewrite),
    corrected = str_glue("{table_figure}, {label}: [[{corrected_value}]]")
  )
# THE DENOMINATOR IS THE CELLS THESE TABLES PRINT, not every claim the ground truth files
# under them. Its rows include in-text sentences filed under the table they quote, and
# counting those puts cells in the denominator that no table has: the article's four
# tables print 681 cells and the ground truth files 713 claims under them. A printed cell
# is the one whose claim_id is built from the table's own grid.
leverage_compared <- ground_truth |>
  filter(table_figure %in% leverage_tables, str_starts(claim_id, "table_")) |>
  nrow()
# A STATE'S OWN STANDARD ERROR, OR A POOLED QUANTITY BUILT OUT OF THEM, which is the
# distinction the note has to draw. Keyed on claim_id, which is the ground truth's stable
# name for a cell, and asserted below: a cell that leaves this list stops the render
# rather than being quietly counted as pooled.
state_level <- c("table_4_presidential_on_midterm_iowa_2004_06_se",
                 "table_5_presidential_on_presidential_kentucky_2008_12_se",
                 "table_6_lower_kentucky_2008_12_se")
leverage_cells <- leverage_cells |> mutate(pooled = !claim_id %in% state_level)
# The Iowa pair is the worked example in the note: the two conventions either side of the
# boundary at which its third decimal turns. Both numbers are computed rather than quoted,
# the deposit's from the archive run and the pipeline's from its own output.
iowa_pipeline <- rd |> filter(state == "IA", years_window == "04-06") |> pull(se)
iowa_deposit  <- 0.0485444288  # sandwich::vcovHC on the AER::ivreg fit, recomputed 2026-09-11
stopifnot(nrow(leverage_cells) == 11,
          all(state_level %in% leverage_cells$claim_id),
          all(str_starts(leverage_cells$claim_id, "table_")),
          round(iowa_pipeline, 3) != round(iowa_deposit, 3))

# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Entry 2's correction is a table row rather than a sentence, so its
# published and corrected fields name the cell that moves and the corrected table is
# reprinted beneath it as a float.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
#
# claim_ids names the ground-truth rows an entry corrects, semicolon-separated, so that
# "is this finding published?" is a query rather than a judgment. It is empty where the
# entry has no ground-truth row: entry 8 is a panel heading in Table A4, whose descriptive
# statistics the extraction does not reach, and entry 9 is a reference list entry, which is
# not an extraction claim. Every id listed here is checked against the ground truth by
# build_ground_truth.R.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids, ~corrected_values,

  1, "quantity", "pipeline", "full",
  "The standard error of the primary-on-primary estimate",
  "published, supporting information",
  "The average estimated primary-on-general CACE is 0.0086 (SE = 0.0236), while the average estimated primary-on-primary CACE is 0.0068 (SE=[[0.0010]]).",
  str_glue("The average estimated primary-on-general CACE is 0.0086 (SE = 0.0236), while the average estimated primary-on-primary CACE is 0.0068 (SE=[[{f4(pp$std_error)}]])."),
  str_glue(
    "The estimate and the other three figures in the sentence reproduce exactly. As ",
    "printed, a standard error of {f4(pp_published_se)} would put the primary-on-primary ",
    "estimate {sprintf('%.1f', pp_z_published)} standard errors from zero, which ",
    "contradicts the sentence's own point that inducement to vote in a primary has ",
    "negligible downstream effects. Recomputed, the estimate is {sprintf('%.2f', pp_z)} ",
    "standard errors from zero, and is indistinguishable from zero as the passage says."),
  "appx_pp_se",
  f4(pp$std_error),

  2, "float", "pipeline", "brief",
  "Appendix Table A2's Iowa row",
  "published, appendix Table A2",
  str_glue("Table A2, {wrong_state$name}, CACE 08-12: [[{iowa_published[['CACE 08-12']]}]]"),
  str_glue("Table A2, {wrong_state$name}, CACE 08-12: [[{f3(round(wrong_state$rd_cace, 3))}]]"),
  str_glue(
    "The changed artifact is the {wrong_state$name} row alone; every other cell is as ",
    "published. The deposited code for this table types its fifteen CACEs in as constants ",
    "rather than reading them from the regression discontinuity output the rest of the ",
    "paper uses, and the constant for {wrong_state$name} is not the estimate that analysis ",
    "produces."),
  "appx_a2_cace_column;table_a2_main_ia_cace_08_12_est;table_a2_main_ia_bias_estimate_est;table_a2_main_ia_corrected_cace_est",
  NA_character_,

  3, "quantity", "pipeline", "full",
  "The count of midterm-on-presidential estimates",
  "published p. 1053",
  "The pattern of midterm-on-presidential estimates argues strongly for habit formation as well. Here, [[50]] out of [[54]] estimates are positive.",
  str_glue("The pattern of midterm-on-presidential estimates argues strongly for habit formation as well. Here, [[{sum(mop$cace > 0)}]] out of [[{nrow(mop)}]] estimates are positive."),
  str_glue(
    "The lower panel of Table 4 prints {nrow(mop)} state estimates, not {nrow(pom)}; the ",
    "upper panel prints {nrow(pom)}, which is the figure the preceding sentence correctly ",
    "gives for the presidential-on-midterm effects. The two panels differ because ",
    "{recode(oregon_only, OR = 'Oregon')} enters the midterm-on-presidential series in ",
    "2006--08 and has no 2004--06 counterpart in the presidential-on-midterm series. Of the ",
    "{nrow(mop)} estimates, {spell(sum(mop$cace < 0))} are negative, so {sum(mop$cace > 0)} ",
    "are positive. Table 4 itself is correct."),
  "rd_mop_positive;rd_mop_estimates",
  str_c(sum(mop$cace > 0), ";", nrow(mop)),

  4, "quantity", "pipeline", "full",
  "Battleground status among the strongest presidential-on-presidential estimates",
  "published p. 1059",
  "The top panel of Table 5, for example, reports 15 estimates of the presidential-on-presidential downstream effect for 2008--12. The top [[four]] of the five strongest estimates (Arkansas, Nevada, Connecticut, Missouri, and New Jersey) are found in nonbattleground states.",
  str_glue("The top panel of Table 5, for example, reports 15 estimates of the presidential-on-presidential downstream effect for 2008--12. The top [[{spell(nrow(nonbattlegrounds_among_five))}]] of the five strongest estimates (Arkansas, Nevada, Connecticut, Missouri, and New Jersey) are found in nonbattleground states."),
  str_glue(
    "Under the article's own coding, a state is a presidential battleground when the ",
    "two-party vote share difference in the downstream election is ten points or fewer. ",
    "{knitr::combine_words(battleground_phrases)} clear that threshold in 2012, so ",
    "{spell(nrow(nonbattlegrounds_among_five))} of the five strongest estimates are in ",
    "nonbattleground states rather than four. The point the sentence makes is unaffected: ",
    "the strongest estimates are not concentrated in battlegrounds."),
  "env_top_four_nonbattleground",
  as.character(nrow(nonbattlegrounds_among_five)),

  5, "quantity", "pipeline", "full",
  "The change in the battleground coefficient between columns 2 and 3 of Table 7",
  "published, main text",
  "When we include the close midterm elections in the definition of battleground, this pattern does not persist---the coefficient drops by a factor of [[three]] and is no longer significant.",
  str_glue("When we include the close midterm elections in the definition of battleground, this pattern does not persist---the coefficient drops by a factor of [[{spell(round(bg_ratio))}]] and is no longer significant."),
  str_glue(
    "Table 7 prints {f4(coefficient('battleground_P', 2, 'estimate'))} in column 2 and ",
    "{f4(coefficient('battleground_PM', 3, 'estimate'))} in column 3, a ratio of ",
    "{sprintf('%.1f', bg_ratio)}. Both cells reproduce exactly; only the description of the ",
    "ratio is wrong, and the coefficient is indeed no longer significant."),
  "env_battleground_factor",
  as.character(round(bg_ratio)),

  6, "quantity", "pipeline", "full",
  "The number of states in Table A2",
  "published, appendix",
  "Table A2 presents the estimated number of net migrants, the estimated number of compliers in 2008 (computed using a 365-day window), and the associated bias according to Equation A10 for [[sixteen]] states.",
  str_glue("Table A2 presents the estimated number of net migrants, the estimated number of compliers in 2008 (computed using a 365-day window), and the associated bias according to Equation A10 for [[{spell(n_a2_states)}]] states."),
  str_glue(
    "The table has {spell(n_a2_states)} rows, one for every state with a 2008-on-2012 ",
    "estimate. Colorado and Michigan have no such estimate, so the analysis covers ",
    "{spell(n_a2_states)} of the seventeen states."),
  "appx_a2_states",
  as.character(n_a2_states),

  7, "cross_reference", "pipeline", "full",
  "The cross-reference for the general-on-general election pairs",
  "published, appendix",
  "Across the 384 general-on-general election pairs (the pairs reported in [[Table 6]] of the main text), the average estimated CACE is 0.101 with a standard error of 0.007.",
  "Across the 384 general-on-general election pairs (the pairs reported in [[Table 7]] of the main text), the average estimated CACE is 0.101 with a standard error of 0.007.",
  str_glue(
    "Table 6 reports {t6_pairs} pairs, every upstream general election on downstream voting ",
    "in 2012. The {gg_pairs} general-on-general pairs are the set Table 7 pools, and Table ",
    "7's own N row prints that figure in all five columns. Both averages in the sentence ",
    "reproduce exactly."),
  "appx_gg_crossref",
  NA_character_,

  8, "label", "pipeline", "brief",
  "The first panel of appendix Table A4",
  "published, appendix Table A4",
  "[[Arizona 2013]]",
  "[[Arkansas 2013]]",
  str_glue(
    "Tables A4 and A5 give descriptive statistics for one panel per voter file, nineteen in ",
    "all: the seventeen states the article analyses plus the two historical files for ",
    "Florida and Missouri. Every other panel corresponds to one of those states. Arkansas is ",
    "one of the seventeen, appears in Tables 4, 5, 6 and A2, and has no panel of its own; ",
    "Arizona appears in no table in the article and is nowhere in the deposited data, whose ",
    "states are {knitr::combine_words(sort(analysis_states))}. The changed artifact is the ",
    "panel heading alone; every figure beneath it is as published."),
  "",
  NA_character_,

  9, "bibliographic", "reference_audit", "brief",
  "Atkinson and Fowler (2014) prints the last page of its range without the first",
  "published p. 1061",
  "Atkinson, Matthew D., and Anthony Fowler. 2014. \"Social Capital and Voter Turnout: Evidence from Saint's Day Fiestas in Mexico.\" British Journal of Political Science [[44(1): 59]].",
  "Atkinson, Matthew D., and Anthony Fowler. 2014. \"Social Capital and Voter Turnout: Evidence from Saint's Day Fiestas in Mexico.\" British Journal of Political Science 44(1): 41--59.",
  paste("Crossref, doi 10.1017/s0007123412000713: pages 41--59. The reference list",
        "abbreviates the second number of a range elsewhere, so a reader has no way to",
        "read \"59\" as anything but a single page."),
  "",
  NA_character_,

  10, "float", "pipeline", "full",
  "The leverage adjustment behind the discontinuity standard errors",
  "published pp. 1054, 1055, 1057, and 1058, and appendix Tables A6 and A7",
  str_c(leverage_cells$published, collapse = "\n\n"),
  str_c(leverage_cells$corrected, collapse = "\n\n"),
  str_glue(
    "Every standard error in the discontinuity tables is heteroskedasticity-robust, and ",
    "the deposited code computes it as coeftest(fit, vcov = vcovHC) on a two-stage least ",
    "squares fit from the AER package. The sandwich package carries no leverage ",
    "convention of its own: it calls hatvalues() on the fit it is handed. AER's method ",
    "for a 2SLS fit returns the diagonal of the asymmetric matrix that maps the outcome ",
    "onto its fitted values, and Belsley, Kuh, and Welsch (1980) considered exactly that ",
    "quantity for 2SLS diagnostics and recommended against it, on the ground that the ",
    "diagonal of an asymmetric matrix is not a leverage. The ivreg package, which now ",
    "carries the implementation AER once did, follows that recommendation and uses the ",
    "second-stage projection, whose diagonal lies between zero and one by construction. ",
    "The maintained pipeline follows the later convention. On the Iowa 2004-06 pair the ",
    "two give {sprintf('%.6f', iowa_deposit)} and {sprintf('%.6f', iowa_pipeline)}, ",
    "either side of the boundary at which the third decimal turns. The difference runs to ",
    "about a part in a thousand, so the published figure stands at the precision these ",
    "tables print in {leverage_compared - nrow(leverage_cells)} of {leverage_compared} ",
    "cells. The {spell(nrow(leverage_cells))} that move are of two kinds. ",
    "{str_to_sentence(spell(sum(!leverage_cells$pooled)))} are a single state's own ",
    "standard error, each sitting on a rounding boundary. The other ",
    "{spell(sum(leverage_cells$pooled))} are pooled quantities that inherit those ",
    "standard errors through a weight: Table 6's meta-analytic estimate is ",
    "precision-weighted by them, Table 7's models are weighted by their inverse squares, ",
    "and every cell of appendix Tables A6 and A7 is a fixed-effects meta-analysis across ",
    "the same states, whose weights are the same standard errors. That is how the ",
    "convention reaches a point estimate, which each state's own estimate is immune to. ",
    "No sentence in the article or the appendix quotes any of the ",
    "{spell(nrow(leverage_cells))}. The appendix's six sit in the tables its Section 2 ",
    "offers as evidence that the estimates are quite robust to specification, and the ",
    "corrected values leave that reading exactly where it was: the 2008-on-2012 estimates ",
    "still cluster between 0.10 and 0.12, the 2006-on-2010 estimates still fall mostly ",
    "between 0.07 and 0.15, and the standard errors still shrink as the window widens."),
  str_c(leverage_cells$claim_id, collapse = ";"),
  NA_character_
) |>
  mutate(across(c(title, published, corrected, note, claim_ids, corrected_values),
                as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# Gate: corrected_values agrees with the sentence it was glued into ----
# The column and the sentence are written from one expression, so they begin in agreement and
# this gate exists for the edit that separates them: a value moved from one marked span to
# another, a span reworded to carry a second number, a claim id appended without its value.
#
# A sentence sets a number the way the page sets it, and this article SPELLS its small
# integers ("the top four", "a factor of three", "sixteen states"). The column sets them as
# the numerals the extraction records, because maintained/in_text_claims.R compares that
# column as a number. The spelling is typography rather than part of the value, so it is
# normalised away before the containment test, along with the en dash and the thousands
# comma; everything else, precision above all, still has to match.
as_compared <- function(x) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten",
             "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", "seventeen",
             "eighteen", "nineteen", "twenty")
  x <- x |>
    str_replace_all("\u2013", "-") |>
    str_replace_all("(?<=\\d),(?=\\d{3})", "")
  reduce(seq_along(words), .init = x,
         \(acc, i) str_replace_all(acc, regex(str_c("\\b", words[i], "\\b"),
                                              ignore_case = TRUE), as.character(i)))
}

marked_spans <- function(x) str_match_all(x, "\\[\\[(.*?)\\]\\]")[[1]][, 2]

quantified <- entries |>
  filter(!is.na(corrected_values)) |>
  mutate(ids = str_split(claim_ids, ";"), values = str_split(corrected_values, ";"),
         spans = map(corrected, marked_spans))

stopifnot(all(lengths(quantified$ids) == lengths(quantified$values)))

value_placed <- pmap_lgl(quantified, function(...) {
  e <- list(...)
  if (length(e$values) == length(e$spans)) {
    all(map2_lgl(e$values, e$spans, \(v, s) str_detect(as_compared(s), fixed(v))))
  } else {
    all(map_lgl(e$values, \(v) any(map_lgl(e$spans, \(s) str_detect(as_compared(s), fixed(v))))))
  }
})

if (!all(value_placed)) {
  print(quantified |> filter(!value_placed) |> select(entry, title, corrected_values, corrected))
  stop("An entry's corrected_values are not in the spans of its corrected sentence.")
}

# An entry that moves a value maintained/in_text_claims.R PRINTS has to say what the value
# becomes, and every other entry carries NA. Only "quantity" does so here. Entry 2 is classed
# "float": it corrects cells of appendix Table A2 and names three float rows the extraction
# does not carry, so no block prints them. Entry 7 corrects a cross-reference whose claim is
# a descriptive one, entries 8 and 9 correct a panel heading and a reference, and entry 10
# corrects five cells of Tables 4 through 7 that no sentence of the article quotes.
stopifnot(
  all(!is.na(entries$corrected_values[entries$class == "quantity"])),
  all(is.na(entries$corrected_values[entries$class != "quantity"])),
  all(is.na(entries$corrected_values) | !is.na(entries$claim_ids))
)

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one.
emit <- function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
}
```

This note lists `r spell(nrow(entries))` corrections to "Is Voting Habit Forming? New Evidence from Experiments and Regression Discontinuities," published in the *American Journal of Political Science* 60(4):1044--1062, doi [10.1111/ajps.12210](https://doi.org/10.1111/ajps.12210). **None of them changes any conclusion of the paper.** One is a standard error, one is a row of an appendix table, six are sentences or a heading that miscount or misdescribe something the article prints correctly, and the last is an entry of the reference list. Everything else in the `r format(n_published_cells, big.mark = ",")` published table cells this note's supporting analysis reads off the page reproduces from the deposited replication archive ([10.7910/DVN/ALZVAW](https://doi.org/10.7910/DVN/ALZVAW)).

Every number in the corrected sentences and in the notes beneath them is computed from the deposited archive at the time this document is rendered. The code and output supporting the corrections are at [github.com/active-maintenance-aec/coppock_green_2016](https://github.com/active-maintenance-aec/coppock_green_2016).

```{r entry-1, results="asis"}
emit(1)
```

```{r entry-2-heading, results="asis"}
# Entry 2's corrected artifact is a table row rather than a sentence, so the entry is set
# around the float instead of as a quoted pair. The moved cell is still read out of the
# spine rather than recomputed here.
e <- entries |> filter(entry == 2)
changed <- function(x) str_match(x, "\\[\\[(.*?)\\]\\]")[, 2]
cat("\n\n## ", e$entry, ". ", e$title, "\n\n",
    "Table A2's CACE 08-12 column holds each state's estimated effect of voting in 2008 on ",
    "voting in 2012, and for ", spell(nrow(a2_check) - nrow(wrong_state)), " of its ",
    spell(nrow(a2_check)), " states it agrees with Tables 5 and 6 exactly. For ",
    wrong_state$name, " it does not: the appendix prints ", changed(e$published),
    ", where Tables 5 and 6 both print ", changed(e$corrected), ". The bias estimate and ",
    "the corrected CACE in that row follow from the wrong figure, so all three cells move. ",
    "The corrected table:\n", sep = "")
```

```{r a2-table}
kable(a2_corrected, booktabs = TRUE, linesep = "", align = "lrrrrr",
      caption = "Table A2 corrected: Migrants, Number of Compliers, and Associated Bias")
```

```{r entry-2-note, results="asis"}
cat(entries$note[entries$entry == 2], "\n", sep = "")
```

```{r entries-3-onward, results="asis"}
walk(entries$entry[entries$entry >= 3 & entries$source == "pipeline"], emit)
```

# The reference list

The entry below corrects the article's reference list. It was found by an audit that sends every printed entry whole to Crossref and checks the authoritative record back into it, and it is verified against the record named in the note. No cited work is missing and no citation in the text points at the wrong work.

```{r reference-entries, results="asis"}
walk(entries$entry[entries$source == "reference_audit"], function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", e$corrected, "\n\n", e$note, "\n", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
